ext_risk_copula

### 2019-02-17 ext_risk_copula.Rmd
models ok, excluding abrewer

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))

@@

  ylm2<-c(-0.04,0.04)
  ## Plot the second plot and put axis scale on right
  plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
       axes=FALSE, type="l", col="orange")
  lines(s$d, s$pop_avg_acf_right, col="skyblue")

@@

  ylm2<-c(-0.04,0.04)
  ## Plot the second plot and put axis scale on right
  plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
       axes=FALSE, type="l", col="orange")
  lines(s$d, s$pop_avg_acf_right, pch=16, col="skyblue")

@@

@@

```{r get_rc_pennycuick,echo=F,cache=T,cache.extra=list(seed,mtime("1var_pop_model_bifurcation.R"))}
source("./1var_pop_model_bifurcation.R")
a_pennycuick<-0.1
b_pennycuick<-0.1
eps<-1e-10 #you can change it upto which decimal point you want it to be exact
rlist<-seq(from=4.3231657,to=4.3231658,by=eps)
res_pennycuick<-c() 
for(r in rlist){
  ans<-fn_d1_eqm(params=c(r,a,b),model="pennycuick")
  res_pennycuick<-c(res_pennycuick,ans)
}

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))

@@

<!--
# Austin Brewer model :

```{r sim_abrewer, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"austinbrewer"
scl<-0.8

numsims<-10000
numsteps<-25
numlocs<-5
s<-0.2
K<-50
p0<-K
rc_abrewer<-1/(K*(1-exp(-s*K)))

rlist<-sort(c(0.002,0.004,0.006,0.008,0.01,0.015,rc_abrewer,0.022,0.026))

abrewer_extrisk_d0<-data.frame(rlist,NA*numeric(length(rlist)),NA*numeric(length(rlist))) #initiate a dataframe to store ext risk at dispersal d=0 for all r
colnames(abrewer_extrisk_d0)<-c("r","risk_left_d0","risk_right_d0")

#for local dispersal in D matrix 
res_abrewer_local<-c()

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,K,s)
    ext_thrs<-p0/10

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_abrewer_local<-abind(res_abrewer_local,temp_mat,along = 3)

    abrewer_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    abrewer_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
}

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_abrewer_local)<-list(NULL,cnm,anm)

saveRDS(abrewer_extrisk_d0,paste(resloc,"abrewer_extrisk_d0.RDS",sep=""))
saveRDS(res_abrewer_local,paste(resloc,"res_abrewer_local.RDS",sep=""))

# For global dispersal in D matrix 
res_abrewer_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,K,s)
    ext_thrs<-p0/10

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_abrewer_global<-abind(res_abrewer_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_abrewer_global)<-list(NULL,cnm,anm)
saveRDS(res_abrewer_global,paste(resloc,"res_abrewer_global.RDS",sep=""))
```

```{r fig_abrewer, echo=F, results="hide",cache=T, cache.extra=list(seed,res_abrewer_local,res_abrewer_global)}
pdf(paste(resloc,"abrewer_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

for(i in 1:dim(res_abrewer_local)[3]){
  s<-res_abrewer_local[,,i]
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))

  ylm2<-c(-0.04,0.04)
  ## Plot the second plot and put axis scale on right
  plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
       axes=FALSE, type="l", col="orange")
  lines(s$d, s$pop_avg_acf_right, col="skyblue")

pdf(paste(resloc,"abrewer_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

for(i in 1:dim(res_abrewer_global)[3]){
  s<-res_abrewer_global[,,i]
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))

  ylm2<-c(-0.04,0.04)
  ## Plot the second plot and put axis scale on right
  plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
       axes=FALSE, type="l", col="orange")
  lines(s$d, s$pop_avg_acf_right, pch=16, col="skyblue")

```{r fig_abrewer_extrisk_d0, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
abrewer_extrisk_d0<-readRDS(paste(resloc,"abrewer_extrisk_d0.RDS",sep=""))

abrewer_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=abrewer_extrisk_d0$risk_left_d0)/numsims
abrewer_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=abrewer_extrisk_d0$risk_left_d0)/numsims
abrewer_extrisk_d0$CI0.025right<-qbinom(p=0.025,size=numsims,prob=abrewer_extrisk_d0$risk_right_d0)/numsims
abrewer_extrisk_d0$CI0.975right<-qbinom(p=0.975,size=numsims,prob=abrewer_extrisk_d0$risk_right_d0)/numsims
pdf(paste(resloc,"abrewer_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(abrewer_extrisk_d0$r,abrewer_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(abrewer_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=abrewer_extrisk_d0$r,y0=abrewer_extrisk_d0$CI0.025left,x1=abrewer_extrisk_d0$r,
       y1=abrewer_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_abrewer,lty="dotted")

lines(abrewer_extrisk_d0$r,abrewer_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=abrewer_extrisk_d0$r,y0=abrewer_extrisk_d0$CI0.025right,
       x1=abrewer_extrisk_d0$r,y1=abrewer_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(0.005,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Austin Brewer model : K = 50, s = 0.2, rc = 0.02000091, scl=0.8) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_abrewer_r_vary_scl_0.8}](./Results/austinbrewer_scl_0.8/abrewer_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Austin Brewer model : K = 50, s = 0.2, rc = 0.02000091, scl=0.8) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_abrewer_r_vary_scl_0.8}](./Results/austinbrewer_scl_0.8/abrewer_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Austin Brewer model with no dispersion : rc=0.02000091, scl=0.8); numlocs=5, numsteps=25, numsims=10000\label{fig_abrewer_risk_d0_scl_0.8}](./Results/austinbrewer_scl_0.8/abrewer_extrisk_d0.pdf){ width=40%, height=40% }
-->

>>>>

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))

@@

  ylm2<-c(-0.2,0.6)
  ## Plot the second plot and put axis scale on right
  plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
       axes=FALSE, type="l", col="orange")
  abline(h=0,lty="dotted",col="grey")
  lines(s$d, s$pop_avg_acf_right, col="skyblue")

@@

  ylm2<-c(-0.2,0.6)
  ## Plot the second plot and put axis scale on right
  plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
       axes=FALSE, type="l", col="orange")
  abline(h=0,lty="dotted",col="grey")
  lines(s$d, s$pop_avg_acf_right, pch=16, col="skyblue")

@@

pdf(paste(resloc,"msmith_ext_risk_global_disp.pdf",sep=""),height=9,width=15)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

@@

```{r get_rc_pennycuick,echo=F,results="hide",cache=T,cache.extra=list(seed,mtime("1var_pop_model_bifurcation.R"))}
source("./1var_pop_model_bifurcation.R")
a_pennycuick<-0.1
b_pennycuick<-0.1
eps<-1e-10 #you can change it upto which decimal point you want it to be exact
rlist<-seq(from=4.3231657,to=4.3231658,by=eps)
res_pennycuick<-c() 
for(r in rlist){
  ans<-fn_d1_eqm(params=c(r,a,b),model="pennycuick")
  res_pennycuick<-c(res_pennycuick,ans)
}

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))

@@
